---
title: "FIN516Project2"
author: "Dushyant Singh Khinchi"
date: "3/7/2020"
output: html_document
---

```{r}

library(quantmod)

y <- read.csv("D:/FIN 516 Derivatives/Project 2/EqFutS20.csv")
# You may need to change formating depending on how your computer reads the date

y$Date <- as.Date(y$Date,'%Y-%m-%d')

# Convert to an xts object
y <- xts(y[,-1],order.by=y[,1])

# Seperate the futures from equity prices


z <- y[,1:4]
eq <- y[,5:ncol(y)]

View(z)
View(eq)
# Create the portfolio where each stock position was equally weighted 1/4/2018
z$port <- eq %*% as.vector( (1/ncol(eq)) / eq[1,])  #here %*% meansmatrix multiplication

View(z$port)

# Portfolio value on 2/10/2020
port <- 250e6 * as.numeric(z$port[nrow(z)])

# Compute log first-differences for futures prices and portfolio value
z <- na.omit(diff(log(z)))
port


sd(z$port)
sd(z$port)*port


```

 Daily standard deviation of returns for the portfolio: 0.01154735
 
 Dollar amount of the daily standard deviation of returns for the portfolio: $4768936
 
 
```{r}
es <- lm(z$port~z$ES)
coef(es)

es.beta <- coef(es)[2]
es.beta

es.r2 <- summary(es)$r.squared
es.r2

#correlation coefficient
sqrt(es.r2)

summary(es)

#Risk reduction factor
1-sqrt(1-es.r2)

#daily standard deviation of hedged returns
sd(z$port)*sqrt(1-es.r2)


#daily standard deviation of hedged returns by dollar value
sd(z$port)*port*sqrt(1-es.r2)

#Varience minimizing number of contracts
N<-port/(50*3338)

#Adjusted for difference in beta
N*es.beta

```
Beta for ES = 1.0505

correlation coefficient for ES = 0.8919

Risk reduction factor for ES = 0.5478

Variance minimizing number of contracts for ES as hedging instrument: 2600

Daily standard deviation of hedged returns by ES contract: 0.0052

Dollar value of daily standard deviation of hedged returns by ES:  $2156392

```{r}
nq <- lm(z$port~z$NQ)
coef(nq)

nq.beta <- coef(nq)[2]
nq.beta

nq.r2 <- summary(nq)$r.squared
nq.r2

summary(nq)

#correlation coefficient
sqrt(nq.r2)

#Risk reduction factor
1-sqrt(1-nq.r2)


#daily standard deviation of hedged returns
sd(z$port)*sqrt(1-nq.r2)

#daily standard deviation of hedged returns by dollar value
sd(z$port)*port*sqrt(1-nq.r2)


#Varience minimizing number of contracts

N<-port/(20*9460)

#Adjusted for difference in beta

N*nq.beta



```
Beta for NQ = 0.8248

Correlation coefficient for NQ = 0.9027

Risk reduction factor for NQ =  0.5698

Variance minimizing number of contracts for NQ as hedging instrument: 1801

Daily standard deviation of hedged returns by NQ contract: 0.0049

Dollar value of daily standard deviation of hedged returns by NQ: $2051334

```{r}
rty <- lm(z$port~z$RTY)
coef(rty)

rty.beta <- coef(rty)[2]
rty.beta

rty.r2 <- summary(rty)$r.squared
rty.r2

summary(rty)

#correlation coefficient
sqrt(rty.r2)

#Risk reduction factor
1-sqrt(1-rty.r2)


#daily standard deviation of hedged returns
sd(z$port)*sqrt(1-rty.r2)


#daily standard deviation of hedged returns by dollar value
sd(z$port)*port*sqrt(1-rty.r2)


#Varience minimizing number of contracts

N<-port/(50*1660)

#Adjusted for difference in beta
N*rty.beta




```
Beta for RTY = 0.8743

Correlation coefficient for RTY = 0.8496

Risk reduction factor for RTY= 0.4726

Variance minimizing number of contracts for RTY as hedging instrument: 4351

Daily standard deviation of hedged returns by RTY: 0.0060

Dollar value of daily standard deviation of hedged returns by RTY: $2514773

```{r}
ixt <- lm(z$port~z$IXT)
coef(ixt)

ixt.beta <- coef(ixt)[2]
ixt.beta

ixt.r2 <- summary(ixt)$r.squared
ixt.r2

summary(ixt)

#correlation coefficient
sqrt(ixt.r2)

#Risk reduction factor
1-sqrt(1-ixt.r2)


#daily standard deviation of hedged returns
sd(z$port)*sqrt(1-ixt.r2)

#daily standard deviation of hedged returns by dollar value
sd(z$port)*port*sqrt(1-ixt.r2)

#Varience minimizing number of contracts
N<-port/(100*1008)

#Adjusted for difference in beta
N*ixt.beta



```
Beta for IXT = 0.7995

Correlation coefficient for IXT = 0.9082

Risk reduction factor for IXT = 0.5815

Variance minimizing number of contracts for IXT as hedging instrument: 3276

Daily standard deviation of hedged returns by IXT contract: 0.0048

Dollar value of daily standard deviation of hedged returns by IXT: $1995794


(f) IXT(E-mini Technology Select Sector) contract should be used for variance-minimizing cross hedge as it offers least risk among all the four contracts with a daily standard deviation of 0.00483
